---
title: "Homework 1"
author: "Jesse Weiss"
date: "January 28, 2018"
output: html_document
---
<style>
body{
background: snow;
}
#header {
    margin: auto;
    width: 50%;
    text-align: center;}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
<ol>
<li> 
<p style = "margin-left: 20px; margin-top:20px; margin-bottom:30px;>The null hypthesis for intercept, tv, radio and newspaper is that there is no relationship between each term and the dependent variable (sales). Additionally, the null hypthesis states that the coefficients for each of these variables are equal to zero. The approximately sero p-value for TV indicates that there is an extremely low probability that TV spend has no association with sales. The same can be said for radio, the near zero p-value indicates an extremely low probability that radio spend has no association with sales. The high p-value for newspaper indicates a lack of evidence that newspaper has any significant relationship with sales when radio and tv spend are held constant.</p>
</li>
<li>
  <ol type = 'a'>
  <li style = 'padding-bottom: 10px;'> iv - For a fixed value of IQ and GPA, females earn more on average than males provided that the GPA is high enough.</li>
  <li style = 'padding-bottom: 10px;'><br />
```{r}

b0 = 50; b1 = 20; b2 = .07; b3 = 35; b4 = .01; b5 = -10

(b0 + b1*4 + b2*110 + b3*1 + b4*4*110 + b5*4*1) * 1000

```
  </li>
  <li> True because an extremely low coefficient is indicative of 
</ol>

</li>
</ol>>